---
title: "Lab Class 2: Rmarkdown"
author: "Change to your name"
subtitle: BUS 696, Fall 2020, Zoom Professor Hersh
output:
  html_document:
    df_print: paged
  html_notebook: default
---

```{r setup, include=FALSE}
library(knitr)


# set seed to your own favorite number
set.seed(1818)
options(width=70)
options(scipen=99)


# general rchunk code options

# this sets text to small
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=TRUE, size = "vsmall")  
opts_chunk$set(message = FALSE,                                          
               warning = FALSE,
               # "caching" stores objects in code chunks and only rewrites if you change things
               cache = TRUE,                               
               # automatically downloads dependency files
               autodep = TRUE,
               # 
               cache.comments = FALSE,
               # 
               collapse = TRUE,
               fig.width = 5,  
               fig.height = 4,
               fig.align='center')


```

this is just text. Here please look at my code below. 

```{r}
library('tidyverse')
data(mpg)
dim(mpg)

```

This is some more text

```{r}
library('ggplot2')
names(mpg)

ggplot(mpg, aes(x = year, y = cty)) + geom_point()
```


## Question 1 
1. Load the `tidyverse` library, and the `mpg` dataset using the command `data(mpg)`. 

2. Use the `glimpse` function to summarize the dataset. 

3. Using the `ggplot2` package create two plots: 1) a scatterplot, and 2) a barplot, using variables of your choosing. 

4. Export (or *compile*) your RMarkdown document to an HTML file.  


```{r}
# if you get an error on loading libraries install package first
# 




```

# Questions 1 a). 

See the graph below which shows that ba

```{r}
# this 


```

# Questions 1 b). 

Here is the different stuff 

```{r}
# this 

library('tidyverse')
data(mpg)
summary(mpg)


ggplot(mpg, aes(x = displ, y = year)) + geom_point()
 
```
